---
title: "FA 2"
author: "Baybayon, Darlyn Antoinette"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### 3.49 Prove that \( \sum_{j=1}^N{(X_{j}-1)^2} = \sum_{j=1}^N{X_{j}^2} - 2 \sum_{j=1}^N{X_{j}} +N  \).

Expand the left-hand side of the equation:

\((X_{j}-1)^2 = (X_{j}^2 - 2X_{j} + 1)\)

By the addition property of summation notation, distribute the summation to all terms in the expression:

\(\sum_{j=1}^N{X_{j}^2} - \sum_{j=1}^N 2{X_{j}} + \sum_{j=1}^N 1  \)

Simplify:


- \(\sum_{j=1}^N{X_{j}} = 2 \sum_{j=1}^N{X_{j}} \) * take out the constant

- \(\sum_{j=1}^N{1} = N \) * since we are adding 1 over N terms, this expression can be rewritten simply as N

Finally, rewrite the equation:

\( \sum_{j=1}^N{(X_{j}-1)^2} = \sum_{j=1}^N{X_{j}^2} - 2 \sum_{j=1}^N{X_{j}} +N  \)

Thus, both sides of the equation are the same.

---

#### 3.51 Two variables, U and V, assume the values \( U_1 = 3, U_2 = - 2, U_3 = 5, \) and \( V_1 = -4, V_2 = -1, \) and \(V_3 = 6\), respectively. Calculate:

##### a) \( \sum{UV} \)

\( \sum{UV} = U_1V_1 + U_2V_2 + U_3V_3\)

\( = (3 \cdot -4) + (-2 \cdot -1) + (5 \cdot 6)\)

\( = (-12) + (2) + (30) \)

\(\sum{UV} \) = **20**



##### b) \( \sum{(U+3)(V-4)} \)

\( \sum{(U+3)(V-4)} = (U_1 + 3)(V_1 - 4) + (U_2 + 3)(V_2 - 4) + (U_3 + 3)(V_3 - 4)\)

\( = (3+3)(-4-4) + (-2+3)(-1-4) + (5+3)(6-4)\)

\( = (6)(-8) + (1)(-5) + (8)(2)\)

\( = (-48) + (-5) + (16)\)

\( \sum{(U+3)(V-4)} = \) **-37**


##### c) \( \sum{V^2} \)

\( \sum{V^2} = V_1^2 + V_2^2 + V_3^2\)

\( = -4 + (-1) + 6\) 

\( \sum{V^2} = \) **1** 

##### d) \( (\sum{U})(\sum{V})^2 \)

\( (\sum{U})(\sum{V})^2 = (U_1 + U_2 + U_3) \cdot (V_1 + V_2 + V_3)^2\)

\( = (3 - 2 + 5) \cdot (-4 - 1 + 6)^2 = 6 \cdot 1^2\)

\( (\sum{U})(\sum{V})^2 = \) **6**

##### e) \( \sum{UV^2} \)

\( \sum{UV^2} = (U_1 \cdot V_1^2) + (U_2 \cdot V_2^2) + (U_3 \cdot V_3^2)\)

\(  = (3 \cdot (-4)^2) + ((-2) \cdot (-1)^2) + (5 \cdot 6^2)\)

\( = (3 \cdot 16) + (-2  \cdot 1) + (5  \cdot 36) = 48 + (-2) + 180\)

\( \sum{UV^2} = \) **226**

##### f) \( \sum{U^2 -2V^2 + 2} \)

\( \sum{U^2 -2V^2 + 2} = [U_1^2 - (2 \cdot V_1^2) + 2] + [U_2^2 - (2 \cdot V_2^2) + 2] + [U_3^2 - (2 \cdot V_3^2) + 2] \)

\( = [3^2 - (2 \cdot (-4)^2) + 2] + [(-2)^2 - (2 \cdot (-1)^2) + 2] + [5^2 - (2 \cdot 6^2) + 2] \)

\( = [9 - (32) + 2] + [4 - (2) + 2] + [25 - (72) + 2] = -21 +  4 - 45\)

\( \sum{U^2 -2V^2 + 2} = \) **-62**


##### g) \( \sum{U/V} \)

\( \sum{U/V} = (\frac{U_1}{V_1}) + (\frac{U_2}{V_2}) + (\frac{U_3}{V_3}) \)

\( = (\frac{3}{-4}) + (\frac{-2}{-1}) + (\frac{5}{6}) \)

\( \sum{U/V} = \frac{7}{12}\)

---

#### 3.90 Find the geometric mean of the sets:
##### a) 3,5,8,3,7,2

\(\text{GM} = \sqrt[6]{3 \cdot 5 \cdot 8 \cdot 3 \cdot 7 \cdot 2}\)
```{r}
gm_a <- (3*5*8*3*7*2)^(1/6)
gm_a

```

##### b) 28.5, 73.6, 47.2, 31.5, 64.8

\(\text{GM} = \sqrt[5]{28.5 \cdot 73.6 \cdot 47.2 \cdot 31.5 \cdot 64.8}\)

```{r}
gm_b <- (28.5*73.6*47.2*31.5*64.8)^(1/5)
gm_b

```
